Ligeti, Stockhausen and Koenig:\\Aesthetics of Electronic Music

### 2015-09-15 manuscript.tex
Some fixes to Ligeti ideas

The following is a curated list musical concepts that I have collected from Ligeti's interview.
The description of each concept is quoted directly from the interview.
I add additional clarification only when absolutely necessary, as I think that the concepts are relatively self-explanatory, in Ligeti's words.

@@

>>>>

The following is a curated list musical concepts that I have collected from Ligeti's interview.
Ligeti was not list his concepts explicitly, hence the categorization is done by me and is also subjective.
The description of each concept is quoted directly from the interview.
I add additional clarification only when absolutely necessary, as I think that the concepts are relatively self-explanatory.

@@

See also the 2\textsuperscript{nd} quote from last subsection (Flexible rhythm -- \ref{subs:ligeti:flexible}).
